---
title: "2017-07-07_Chapter_2_SSU_IntialClean"
Author: Michala Phillips
Cleans OTU tables and sorts them by functional group and family. 
output: html_notebook

Load Required Packages
```{r}
library(dplyr)
library(reshape2)
library(ggplot2)
```
Set wd and import data files
```{r}
setwd("D:/R_Workspace/Amplicon_stuff/Chapter_2_NAUData/data/SSU_redo")
ssu<-read.csv("SSU_Redo_CSS_table_sorted_with_metadata1.csv")
metassu<-read.csv("MP_SSU_MAP.csv")
```
Rename SSU hedings
```{r}
names(ssu)[names(ssu)=="ï...OTU.ID"] <- "ssuotu"
names(ssu)[names(ssu)=="taxonomy"] <- "ssutaxonomy"
names(ssu)[names(ssu)=="Kingdom"] <- "ssukingdom"
names(ssu)[names(ssu)=="Phylum"] <- "ssuphylum"
names(ssu)[names(ssu)=="Class"] <- "ssuclass"
names(ssu)[names(ssu)=="Order"] <- "ssuorder"
names(ssu)[names(ssu)=="Family"] <- "ssufamily"
names(ssu)[names(ssu)=="Genus"] <- "ssugenus"
names(ssu)[names(ssu)=="Species"] <- "ssuspecies"

#remove Geosiphonaceae
drop.family <- c(
"Geosiphonaceae"
)
ssu  <- ssu[-which(ssu$ssufamily %in% drop.family),]

drop <-c("No blast hit")
ssu  <- ssu[-which(ssu$ssutaxonomy %in% drop),]

```
Add in functional groups 
```{r}
for (i in 1:595){
  
if (ssu$ssufamily[i]=="Glomeraceae") {
  ssu$Functional.Group[i]<-"Rhizophilic"
} else if ( ssu$ssufamily[i]=="Claroideoglomeraceae") {
  ssu$Functional.Group[i]<-"Rhizophilic"
} else if(ssu$ssufamily[i]=="Gigasporaceae"){
  ssu$Functional.Group[i]<-"Edaphophilic"
} else if(ssu$ssufamily[i]=="Diversisporaceae") {
  ssu$Functional.Group[i]<-"Edaphophilic"
} else if (ssu$ssufamily[i]=="Paraglomeraceae") {
  ssu$Functional.Group[i]<-"Rhizophilic"
} else if(ssu$ssufamily[i]=="Ambisporaceae"){
  ssu$Functional.Group[i]<-"Ancestral"
} else if(ssu$ssufamily[i]=="Archaeosporaceae"){
  ssu$Functional.Group[i]<-"Ancestral"
} else if(ssu$ssufamily[i]=="Acaulosporaceae"){
  ssu$Functional.Group[i]<-"Ancestral"
} 

}
  
```
Take data from wide to long and renaming variables
```{r}
ssul <-melt(ssu)
names(ssul)[names(ssul)=="variable"] <- "ID"
names(ssul)[names(ssul)=="value"] <- "ssureads"

```
Functional group OTU richnesses and read abundance for each functional group I LIKE THIS WAY A LOT BECAUSE YOU CAN NAME THE ACTUAL HEADERS

Below is in format for graphing
```{r}
ssuguildREADRICH<- data.frame(ssul %>%
                                group_by(ID,Functional.Group) %>%
                                summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
                                         Read_Abundance_Sample = sum(ssureads)
                                ) 
                              
)


```

Make SSU data frame with family level OTU richness and Read abundance for each family
```{r}
ssufamily <- data.frame(ssul %>%
                          group_by(ID, ssufamily) %>%
                          summarise(Family_OTU_Richness = length(unique(ssuotu[ssureads>0])), 
                                    Family_Read_Abundance = sum(ssureads)
                          ))


```
Add metadata into ssu family
```{r}
names(metassu)[names(metassu)=="SAMPLEID2"] <- "ID"
ssufamily<-merge(ssufamily,metassu, by="ID")
ssul<-merge(ssul,metassu,by="ID")

```
Adds meta data to data for box plot

```{r}
ssuguildREADRICH<-merge(ssuguildREADRICH,metassu, by="ID")
#write.csv(ssuguildREADRICH, file = "2017_25_09_ssu_funcguild_read_rich.csv")
###For ssufamily, moves ID to single line and family to the length
LssufamilyOTURICH <- dcast(ssufamily, ID ~ ssufamily, value.var = "Family_OTU_Richness",  fun.aggregate = sum )
LssufamilyOTUREAD <- dcast(ssufamily, ID ~ ssufamily, value.var = "Family_Read_Abundance",  fun.aggregate = sum )

```

Functional group read and richness together
```{r} 
ssuguildREADRICHlong<- data.frame(ssul %>%
                                group_by(ID) %>%
                                summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
                                Ancestral_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Ancestral"])),
                                Edaphophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Edaphophilic"])),
                                Rhizophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Rhizophilic"])),
                                Ancestral_Read_Abundance = sum(ssureads[Functional.Group == "Ancestral"]),
                                Edaphophilic_Read_Abundance = sum(ssureads[Functional.Group == "Edaphophilic"]),
                                Rhizophilic_Read_Abundance = sum(ssureads[Functional.Group == "Rhizophilic"]),
                                Read_Abundance_Sample = sum(ssureads)
                                ) 
                              )

ssuguildREADRICHlong <- merge(ssuguildREADRICHlong, metassu, by = "ID")                             
#write.csv(ssuguildREADRICHlong, file = "2017_25_09_ssu_funcguild_read_rich.csv")
```
Functional group read and richness separate 
```{r}
ssuguildREAD<- data.frame(ssul %>%
                            group_by(ID) %>%
                            summarise(Ancestral_Read_Abundance = sum(ssureads[Functional.Group == "Ancestral"]),
                            Edaphophilic_Read_Abundance = sum(ssureads[Functional.Group == "Edaphophilic"]),
                            Rhizophilic_Read_Abundance = sum(ssureads[Functional.Group == "Rhizophilic"])
                            ) 
                          )

ssuguildRICH<- data.frame(ssul %>%
                            group_by(ID) %>%
                            summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
                            Ancestral_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Ancestral"])),
                            Edaphophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Edaphophilic"])),
                            Rhizophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Rhizophilic"]))
                            ) 
                          )
```
Add metadata to above 
```{r}
ssuguildRICH<-merge(ssuguildRICH, metassu, by="ID")
ssuguildREAD<-merge(ssuguildREAD, metassu, by="ID")
```

Separating data by root and soil
```{r}
ssuroot.readreach<-subset(ssuguildREADRICH,ssuguildREADRICH$TYPE == "ROOT")
ssuguildREADRICHlong<-merge(ssuguildREADRICHlong,metassu,by="ID")
ssuroot.readreachlong<-subset(ssuguildREADRICHlong,ssuguildREADRICHlong$TYPE == "ROOT")
#soil
ssusoil.readreach<-subset(ssuguildREADRICH,ssuguildREADRICH$TYPE == "SOIL")
ssuguildREADRICHlong<-merge(ssuguildREADRICHlong,metassu,by="ID")
ssusoil.readreachlong<-subset(ssuguildREADRICHlong,ssuguildREADRICHlong$TYPE == "SOIL")
```
Pull out roots and soil for Family DFs
```{r}
ssufamroot<-subset.data.frame(ssufamily,TYPE == "ROOT")
names(ssufamroot)[names(ssufamroot)=="ssufamily"]<-"Family"
ssufamsoil<-subset.data.frame(ssufamily,TYPE == "SOIL")
names(ssufamsoil)[names(ssufamsoil)=="ssufamily"]<-"Family"
```
