---
title: "AMF"
author: "C. Nell"
date: '20180821'
output:
  html_document: default
  pdf_document: default
---  

### Logic   
  Salvage topsoil was removed from a donor site and delivered to three recipient sites in 2015. We sampled all sites (Donor and recipients) prior to topsoil delivery and sequenced AM Fungi from all sites in 2015 and 2017 from manipulative plots, set up in a randomized block design at each site with: control treatments (no topsoil added), a dusting of topsoil, and three levels of topsoil thicknesses (2", 4" and 6" thick layers of this topsoil, originating from the donor site)), delivered to all recipient sites).
```{r, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, tidy=TRUE, error = FALSE, eval = TRUE, message = FALSE, warning = FALSE, rows.print=5, cols.min.print=4, fig.width=6, fig.height=4.5)
```
### Questions:
###**Q1: 
  Propagule determination: Do AM fungal communities resemble the donor site, regardless of where soil was delivered? Is provenance a driver of AM fungal community composition?

###**Q2: 
  Environmental filtering: Do AM fungal communities resemble the recipient sites, and are more dissimilar to the AM fungal communities from the donor site?

###**Q3: 
  Propagule pressure: Do AM fungal communities resemble the donor site more in higher level topsoil treatments, than they do in the control or dusted sites?
  
####**Outputs:** 

#Analysis of similarity:

  Determine the similarity of AMF communities at each recipient site to the donor site, from where topsoils originated from. 
    Generate heatmaps with distances, to visually determine - which sites/samples are more similar to each other, and which are more dissimilar. 
    Generate NMDS / Pcoa, plotted with Year as shapes and Sites as colors, and Description as ...?
    Run permanova
      Do AM fungal communities at each site resemble the recipient sites, and are they more dissimilar to the donor sites?
      
#Functional group richness:

  Determine the richness of AMF functional groups in the donor site, from where topsoils originated from, and in the recipient sites pre-topsoil delivery (pre-treatment), and post-topsoil delivery (post-treatment)
  
#Taxonomic diversity:

  Determine the OTU taxa richness (alpha diversity) of AMF communities in the donor site, from where topsoils originated from, and in the recipient sites pre-topsoil delivery (pre-treatment), and post-topsoil delivery (post-treatment).
  Determine the beta diversity of AMF communities in the donor site, from where topsoils originated from, and in the recipient sites pre-topsoil delivery (pre-treatment), and post-topsoil delivery (post-treatment).
  
#Topsoil level treatments

  Propagule pressure: Do AM fungal communities resemble the donor site more in thicker topsoil layer treatments than they do in the control or dusted sites?
  Are the sites with Treat groups = S, more similar to the donor site than F, and are treatment groups S and F more similar to the donor site than T? Is this relationship clinal, with S being the thickest and most similar to donor site, followed by F, and then by T.
  TO FIGURE OUT - how to address this question statistically??multiple regression with Treat on the X and similarity to Donor Site on the Y?? A permanova with multiple comparisons?
  
```{r}
knitr::opts_chunk$set(cache=TRUE, tidy=TRUE, error = FALSE, eval = TRUE, message = FALSE, warning = FALSE, rows.print=5, cols.min.print=4, fig.width=6, fig.height=4.5)
```
Load Required Packages
```{r}
library(tidyverse)
library(dplyr) ## for data wrangling - %>% function
library(reshape2)  ##melt and cast data
library(ggplot2) # plotting
library(data.table)
library(stringr)
library(tidyr) # 'separate' function
library(readxl) #read xlsx files into r on mac computer
library(vegan) # dissimilarity matrix, permanova functions
library(magrittr)
library(cowplot)
library(formatR)


date<-format(Sys.time(), '%Y%b%d')
date

```

** the following is adapted from 2017-07-07_Chapter_2_SSU_IntialClean **  

Import data files
```{r}
# read in OTU table
ssu<-fread('CSS_table_sorted.txt')
str(ssu)

## mapping data
metassu<-fread('map_SSU_Salvage_qiimeformat.txt', header=TRUE)
metassu$Year<-as.character(metassu$Year)
metassu$Rep<-as.factor(metassu$Rep)
str(metassu)
```
Clean SSU headers  
```{r}
colnames(ssu)
head(ssu$taxonomy)

# rename columns
names(ssu)[1] <- 'ssuotu' #rename first column
names(ssu)[names(ssu)=='taxonomy'] <- 'ssutaxonomy' # rename column that is currently called taxonomy

# split taxonomy column
?str_match
ssu$ssukingdom<-str_match(ssu$ssutaxonomy, "k__(.*?);")[,2]
ssu$ssuphylum<-str_match(ssu$ssutaxonomy, "p__(.*?);")[,2]
ssu$ssuclass<-str_match(ssu$ssutaxonomy, "c__(.*?);")[,2]
ssu$ssuorder<-str_match(ssu$ssutaxonomy, "o__(.*?);")[,2]
ssu$ssufamily<-str_match(ssu$ssutaxonomy, "f__(.*?);")[,2]
ssu$ssugenus<-str_match(ssu$ssutaxonomy, "g__(.*?);")[,2]
ssu$ssuspecies<-str_match(ssu$ssutaxonomy, "s__(.*?)")[,2]

colnames(ssu)
ssu.save<-ssu

#remove Geosiphonaceae
unique(ssu$ssufamily)
drop.family <- c("Geosiphonaceae")
ssu  <- ssu[-which(ssu$ssufamily %in% drop.family),]

#remove no blast hits
unique(ssu$ssutaxonomy)
drop <-c("No blast hit")
ssu  <- ssu[-which(ssu$ssutaxonomy %in% drop),]

## alternatively, can use filtering to drop these and avoid rewriting things 
ssu <- ssu.save%>%filter(ssufamily != "Geosiphonaceae" & ssutaxonomy != "No blast hit")

```
Add in functional groups 

```{r}
# this does the same as above but avoids hard coding names, more generalized
ssu.fg <- ssu %>%
  mutate(Functional.Group = case_when(
    ssufamily %in% c('Glomeraceae','Claroideoglomeraceae', 'Paraglomeraceae') ~ 'Rhizophilic',
    ssufamily %in% c('Gigasporaceae', 'Diversisporaceae') ~ 'Edaphophilic',
    ssufamily %in% c('Ambisporaceae', 'Archaeosporaceae','Acaulosporaceae') ~ 'Ancestral'
  ))

```
Take data from wide to long and renaming variables
```{r}
ssul <-melt(ssu.fg, variable.name='ID',value.name='ssureads')
str(ssul) 

```
Functional group OTU richnesses and read abundance for each functional group 

Below is in format for graphing
```{r}
ssuguildREADRICH<- data.frame(ssul %>%
                                group_by(ID,Functional.Group) %>%
                                summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
                                         Read_Abundance_Sample = sum(ssureads)))


```

Make SSU data frame with family level OTU richness and Read abundance for each family
```{r}
ssufamily <- data.frame(ssul %>%
                          group_by(ID, ssufamily) %>%
                          summarise(Family_OTU_Richness = length(unique(ssuotu[ssureads>0])), 
                                    Family_Read_Abundance = sum(ssureads)))

```
Add metadata into ssu family
```{r}
colnames(metassu) # need to edit for appropriate headers
names(metassu)[names(metassu) == 'SampleID2'] <- 'ID'

ssufamily<-ssufamily%>%
  left_join(metassu, by='ID')
str(ssufamily)

ssuguildREADRICH<-ssuguildREADRICH%>%
  left_join(metassu, by='ID')
str(ssuguildREADRICH)  

filename<-paste0(date, '_ssu_funcguild_read_rich.csv')
write.csv(ssuguildREADRICH, file = filename, row.names=FALSE)

```
Adds meta data to data for box plot

```{r}
###For ssufamily, moves ID to single line and family to the length
LssufamilyOTURICH <- dcast(ssufamily, ID ~ ssufamily, value.var = "Family_OTU_Richness",  fun.aggregate = sum )
LssufamilyOTUREAD <- dcast(ssufamily, ID ~ ssufamily, value.var = "Family_Read_Abundance",  fun.aggregate = sum )

head(LssufamilyOTUREAD)
```

Functional group read and richness together
```{r} 
ssuguildREADRICHlong<- data.frame(ssul %>%
                                group_by(ID) %>%
                                summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
                                Ancestral_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Ancestral"])),
                                Edaphophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Edaphophilic"])),
                                Rhizophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Rhizophilic"])),
                                Ancestral_Read_Abundance = sum(ssureads[Functional.Group == "Ancestral"]),
                                Edaphophilic_Read_Abundance = sum(ssureads[Functional.Group == "Edaphophilic"]),
                                Rhizophilic_Read_Abundance = sum(ssureads[Functional.Group == "Rhizophilic"]),
                                Read_Abundance_Sample = sum(ssureads)))
View(ssuguildREADRICHlong)
ssuguildREADRICHlong <- merge(ssuguildREADRICHlong, metassu, by = "ID")

filename<-paste0(date, '_ssu_funcguild_read_rich.csv')
write.csv(ssuguildREADRICHlong, file = filename, row.names=FALSE)

str(ssuguildREADRICHlong)
```

Functional group read and richness separate 
```{r}

ssuguildREAD <- ssul %>% 
  group_by(ID) %>%
  summarise(Ancestral_Read_Abundance = sum(ssureads[Functional.Group == "Ancestral"]),
            Edaphophilic_Read_Abundance = sum(ssureads[Functional.Group == "Edaphophilic"]),
            Rhizophilic_Read_Abundance = sum(ssureads[Functional.Group == "Rhizophilic"]))


ssuguildRICH<- ssul %>%
  group_by(ID) %>%
  summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
            Ancestral_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Ancestral"])),
            Edaphophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Edaphophilic"])),
            Rhizophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Rhizophilic"]))) 
head(ssuguildRICH)
```
Add metadata to above 
#Everytime I run this the output is different, sometime it merges the data with the metadata with two copies of the metadata (e.g., Site.x and Site.y)
#To address this, DON'T RUN NEXT CHUNK WITHOUT RERUNNING THE PREVIOUS CHUNK GENERATING THE ORIGINAL ssuguildRICH FILE, WITHOUT THE METADATA, tried to use "all.y = FALSE" after merge(ssuguildRICH, metassu, by="ID",""
```{r}
ssuguildRICH<-merge(ssuguildRICH, metassu, by="ID", all.y = FALSE)
ssuguildREAD<-merge(ssuguildREAD, metassu, by="ID", all.y = FALSE)
str(ssuguildRICH)
str(ssuguildREAD)
View(ssuguildREAD)
```
Examining the statistic support for increased rhizophilic richness in recipientpost plots
```{r glm on Rhizophilic richness and metadata}
y<-ssuguildRICH$Rhizophilic_Richness
str(y)
D<-ssuguildRICH$Description
S<-ssuguildRICH$Site

length(S)
length(D)
?lm
#lm(y~D)
str(SRhizRich)
SRhizRich<-lm(y ~ S)


DRhizRich<-lm(y~D)
str(DRhizRich)

DSRhizRich<-lm(y~S*D)
str(DSRhizRich)

summary(DSRhizRich)

y<-ssuguildRICH$Rhizophilic_Richness
str(y)
D<-ssuguildRICH$Description
S<-ssuguildRICH$Site
length(S)
length(D)
?lm

glm(y~D)
G_SRhizRich<-glm(y~S)
str(G_SRhizRich)

G_DRhizRich<-glm(y~D)
str(G_DRhizRich)
summary(G_DRhizRich)

DSRhizRich<-lm(y~S*D)
str(DSRhizRich)

summary(DSRhizRich)
lm(y~D*S)
lm(y~D+S)
?glm
glm(y ~ D)

 #Description+Site

```
**start '2017_16_07_SSU_Boxplots.R'** 
Plotting
```{r}
#richness
plot.df<-ssuguildREADRICH
str(plot.df)

richbox <- ggplot(plot.df, aes(x = Functional.Group , y = OTU_Richness_Sample)) + geom_boxplot(aes(fill = Description)) 
richbox

richbox <- richbox + theme_bw(base_size = 15) + xlab("Functional Group") +ylab("AMF Taxa Richness")    
richbox

richbox <-richbox + scale_fill_manual(values=c('red', 'darkslateblue','gold3'))
richbox
```  
```{r, eval=FALSE}
##reads
plot.read<-ssuguildREADRICH
str(plot.read)

reachbox <- ggplot(plot.read, aes(x = Functional.Group, y = OTU_Richness_Sample)) + geom_boxplot(aes(fill = Description)) 
reachbox

reachbox <- reachbox + theme_bw(base_size = 15) + xlab("Functional Group") +ylab("AMF Taxa Reads")    
reachbox

reachbox <-reachbox + scale_fill_manual(values=c('red', 'darkslateblue','gold3'))
reachbox
```

```
#Working on examining other variables 

```{r}
plot.df<-ssuguildREADRICH
str(plot.df)

richbox <- ggplot(plot.df, aes(x = Functional.Group , y = OTU_Richness_Sample)) + geom_boxplot(aes(fill = Description)) 
richbox

richbox <- richbox + theme_bw(base_size = 15) + xlab("Functional Group") +ylab("AMF Taxa Richness")    
richbox

richbox <-richbox + scale_fill_manual(values=c('red', 'darkslateblue','gold3'))
richbox

```
