---
title: "AMF"
author: "C. Nell"
date: '20180817'
output:
  html_document: default
  pdf_document: default
---  

###Questions:
#### Q1: Propagule determination: Do AM fungal communities resemble the donor site, irregardless of where soil was delivered?
#### Q2: Environmental filtering: Do AM fungal communities resemble the recipient sites, and are more dissimilar to the donor sites
#### Q3: Propagule pressure: Do AM fungal communities resemble the donor site more in thicker topsoil layer treatments than they do in the control or dusted sites?

```{r, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, tidy=TRUE, error = FALSE, eval = TRUE, message = FALSE, warning = FALSE, rows.print=5, cols.min.print=4, fig.width=6, fig.height=4.5)
```
Load Required Packages
```{r}
library(tidyverse)
library(dplyr)
library(reshape2)
library(ggplot2)
library(data.table)
library(stringr)

date<-format(Sys.time(), '%Y%b%d')
date

```

** the following is adapted from 2017-07-07_Chapter_2_SSU_IntialClean **  

Import data files
```{r}
# read in OTU table
ssu<-fread('CSS_table_sorted.txt')
str(ssu)

## mapping data
metassu<-fread('map_SSU_Salvage_qiimeformat.txt', header=TRUE)
metassu$Year<-as.character(metassu$Year)
metassu$Rep<-as.factor(metassu$Rep)
str(metassu)
```
Clean SSU headers  
```{r}
colnames(ssu)
head(ssu$taxonomy)

# rename columns
names(ssu)[1] <- 'ssuotu' #rename first column
names(ssu)[names(ssu)=='taxonomy'] <- 'ssutaxonomy' # rename column that is currently called taxonomy

# split taxonomy column
?str_match
ssu$ssukingdom<-str_match(ssu$ssutaxonomy, "k__(.*?);")[,2]
ssu$ssuphylum<-str_match(ssu$ssutaxonomy, "p__(.*?);")[,2]
ssu$ssuclass<-str_match(ssu$ssutaxonomy, "c__(.*?);")[,2]
ssu$ssuorder<-str_match(ssu$ssutaxonomy, "o__(.*?);")[,2]
ssu$ssufamily<-str_match(ssu$ssutaxonomy, "f__(.*?);")[,2]
ssu$ssugenus<-str_match(ssu$ssutaxonomy, "g__(.*?);")[,2]
ssu$ssuspecies<-str_match(ssu$ssutaxonomy, "s__(.*?)")[,2]

colnames(ssu)
ssu.save<-ssu

#remove Geosiphonaceae
unique(ssu$ssufamily)
drop.family <- c("Geosiphonaceae")
ssu  <- ssu[-which(ssu$ssufamily %in% drop.family),]

#remove no blast hits
unique(ssu$ssutaxonomy)
drop <-c("No blast hit")
ssu  <- ssu[-which(ssu$ssutaxonomy %in% drop),]

## alternatively, can use filtering to drop these and avoid rewriting things 
ssu <- ssu.save%>%filter(ssufamily != "Geosiphonaceae" & ssutaxonomy != "No blast hit")

```
Take out functional groups 
#
ssu wide dataframe with lots of cols for taxonomy

#
```{r head of ssu}
head(ssu)
```
Take data from wide to long and renaming variables
```{r}
ssul <-melt(ssu, variable.name='ID',value.name='ssureads')
str(ssul) 

```
Functional group OTU richnesses and read abundance for each functional group 

Below is in format for graphing
```{r}
ssuguildREADRICH<- data.frame(ssul %>%
                                group_by(ID,ssufamily) %>%
                                summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
                                         Read_Abundance_Sample = sum(ssureads)))


```

Make SSU data frame with family level OTU richness and Read abundance for each family
```{r}
ssufamily <- data.frame(ssul %>%
                          group_by(ID, ssufamily) %>%
                          summarise(Family_OTU_Richness = length(unique(ssuotu[ssureads>0])), 
                                    Family_Read_Abundance = sum(ssureads)))

```
Add metadata into ssu family
```{r}
colnames(metassu) # need to edit for appropriate headers
names(metassu)[names(metassu) == 'SampleID2'] <- 'ID'

ssufamily<-ssufamily%>%
  left_join(metassu, by='ID')
str(ssufamily)

ssuguildREADRICH<-ssuguildREADRICH%>%
  left_join(metassu, by='ID')
str(ssuguildREADRICH)  

filename<-paste0(date, '_ssu_funcguild_read_rich.csv')
write.csv(ssuguildREADRICH, file = filename, row.names=FALSE)

```
Adds meta data to data for box plot

```{r}
###For ssufamily, moves ID to single line and family to the length
LssufamilyOTURICH <- dcast(ssufamily, ID ~ ssufamily, value.var = "Family_OTU_Richness",  fun.aggregate = sum )
LssufamilyOTUREAD <- dcast(ssufamily, ID ~ ssufamily, value.var = "Family_Read_Abundance",  fun.aggregate = sum )

head(LssufamilyOTUREAD)
```

NOTFunctional group read and richness together
TaxaReadRich
```{r} 
ssutaxaREADRICHlong<- data.frame(ssul %>%
                                group_by(ID) %>%
                                summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
                                Read_Abundance_Sample = sum(ssureads)))
View(ssutaxaREADRICHlong)
ssutaxaREADRICHlong <- merge(ssutaxaREADRICHlong, metassu, by = "ID")

filename<-paste0(date, '_ssu_taxa_read_rich.csv')
write.csv(ssutaxaREADRICHlong, file = filename, row.names=FALSE)

str(ssutaxaREADRICHlong)
```

Functional group read and richness separate

WORK ON THIS!!
```{r}
ssutaxaREAD <- ssul %>% 
  group_by(ID) %>%
  summarise(Ancestral_Read_Abundance = sum(ssureads[Functional.Group == "Ancestral"]),
            Edaphophilic_Read_Abundance = sum(ssureads[Functional.Group == "Edaphophilic"]),
            Rhizophilic_Read_Abundance = sum(ssureads[Functional.Group == "Rhizophilic"]))


ssuguildRICH<- ssul %>%
  group_by(ID) %>%
  summarise(OTU_Richness_Sample = length(unique(ssuotu[ssureads>0])),
            Ancestral_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Ancestral"])),
            Edaphophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Edaphophilic"])),
            Rhizophilic_Richness = length(unique(ssuotu[ssureads>0 & Functional.Group =="Rhizophilic"]))) 
head(ssuguildRICH)
```
Add metadata to above 
```{r}
ssuguildRICH<-merge(ssuguildRICH, metassu, by="ID")
ssuguildREAD<-merge(ssuguildREAD, metassu, by="ID")
str(ssuguildRICH)
str(ssuguildREAD)
```
```{r glm on Rhizophilic richness and metadata}
y<-ssuguildRICH$Rhizophilic_Richness
str(y)
D<-ssuguildRICH$Description
S<-ssuguildRICH$Site

length(S)
length(D)
?lm
#lm(y~D)
SRhizRich<-lm(y ~ S)
str(SRhizRich)

DRhizRich<-lm(y~D)
str(DRhizRich)

DSRhizRich<-lm(y~S*D)
str(DSRhizRich)

summary(DSRhizRich)

y<-ssuguildRICH$Rhizophilic_Richness
str(y)
D<-ssuguildRICH$Description
S<-ssuguildRICH$Site
length(S)
length(D)
?lm

glm(y~D)
G_SRhizRich<-glm(y~S)
str(G_SRhizRich)

G_DRhizRich<-glm(y~D)
str(G_DRhizRich)
summary(G_DRhizRich)

DSRhizRich<-lm(y~S*D)
str(DSRhizRich)

summary(DSRhizRich)
lm(y~D*S)
lm(y~D+S)
?glm
glm(y ~ D)

 #Description+Site

```




**Does not apply below**  

Separating data by root and soil
```{r, eval=FALSE, include=FALSE}
## issue
## TYPE does not exist in data

# root
ssuroot.readreach<-subset(ssuguildREADRICH,ssuguildREADRICH$TYPE == "ROOT")
ssuguildREADRICHlong<-merge(ssuguildREADRICHlong,metassu,by="ID")
ssuroot.readreachlong<-subset(ssuguildREADRICHlong,ssuguildREADRICHlong$TYPE == "ROOT")
#soil
ssusoil.readreach<-subset(ssuguildREADRICH,ssuguildREADRICH$TYPE == "SOIL")
ssuguildREADRICHlong<-merge(ssuguildREADRICHlong,metassu,by="ID")
ssusoil.readreachlong<-subset(ssuguildREADRICHlong,ssuguildREADRICHlong$TYPE == "SOIL")

```
Pull out roots and soil for Family DFs
```{r, include=FALSE, eval=FALSE}
ssufamroot<-subset.data.frame(ssufamily,TYPE == "ROOT")
names(ssufamroot)[names(ssufamroot)=="ssufamily"]<-"Family"
ssufamsoil<-subset.data.frame(ssufamily,TYPE == "SOIL")
names(ssufamsoil)[names(ssufamsoil)=="ssufamily"]<-"Family"
```


Plotting  
**start '2017_16_07_SSU_Boxplots.R'** 
```{r}
#richness
plot.df<-ssuguildREADRICH
str(plot.df)

richbox <- ggplot(plot.df, aes(x = Functional.Group , y = OTU_Richness_Sample)) + geom_boxplot(aes(fill = Description)) 
richbox

richbox <- richbox + theme_bw(base_size = 15) + xlab("Functional Group") +ylab("AMF Taxa Richness")    
richbox

richbox <-richbox + scale_fill_manual(values=c('red', 'darkslateblue','gold3'))
richbox
```  
```{r, eval=FALSE}
##reads
plot.read<-ssuguildREAD
str(plot.read)

#reachbox <- ggplot(plot.read, aes(x = Functional.Group , y = OTU_Richness_Sample)) + geom_boxplot(aes(fill = Description)) 
reachbox

reachbox <- reachbox + theme_bw(base_size = 15) + xlab("Functional Group") +ylab("AMF Taxa Reads")    
reachbox

reachbox <-reachbox + scale_fill_manual(values=c('red', 'darkslateblue','gold3'))
reachbox

```